### 2024-12-01 paper/paper.qmd
change box-plot to violin-plot for better visualization

boxplot_plot_clarity <- ggplot(cleaned_data, aes(x = clarity, y = price)) +
  geom_boxplot(fill = "lightblue",outlier.color = "salmon", outlier.shape = 8, alpha = 0.7) +
  labs(
    title = "Boxplot of Price by Clarity",
    x = "Cut",
    y = "Price"
  ) +
  theme_minimal()

# Combine 2 plots
combined_plot <- clarity_histogram_plot | boxplot_plot_clarity
combined_plot

@@

violin_plot_cut <- ggplot(cleaned_data, aes(x = cut, y = price)) +
  geom_violin(trim = FALSE, fill = "lightblue", alpha = 0.7) + 
  geom_boxplot(width = 0.2, outlier.cut = "salmon", outlier.shape = 8, alpha = 0.7) +
  labs(
    title = "Violin Plot of Price by Cut",
    x = "Cut",
    y = "Price"
  ) +
  theme_minimal()

>>>>

violin_plot_clarity <- ggplot(cleaned_data, aes(x = clarity, y = price)) +
  geom_violin(trim = FALSE, fill = "lightblue", alpha = 0.7) + 
  geom_boxplot(width = 0.2, outlier.color = "salmon", outlier.shape = 8, alpha = 0.7) +
  labs(
    title = "Violin Plot of Price by Clarity",
    x = "Clarity",
    y = "Price"
  ) +
  theme_minimal()

# Combine 2 plots
combined_plot <- clarity_histogram_plot | violin_plot_clarity
combined_plot

@@

violin_plot_cut <- ggplot(cleaned_data, aes(x = cut, y = price)) +
  geom_violin(trim = FALSE, fill = "lightblue", alpha = 0.7) + 
  geom_boxplot(width = 0.2, outlier.color = "salmon", outlier.shape = 8, alpha = 0.7) +
  labs(
    title = "Violin Plot of Price by Cut",
    x = "Cut",
    y = "Price"
  ) +
  theme_minimal()
